### 2021-02-10 treatise-pdflatex/4_simulation.tex
Rev contribution

\DispNum {y:y:Ry:Ny} {
\tilde {\V {y}}
= \mathcal {R} \SB {\V {y}}
\in \mathbb {R} ^{2 N_B^2} \\
%
\tilde {\V {g}}
= \mathcal {R} \SB {\V {g}}
\in \mathbb {R} ^{2 N_H^2} \\
%
\tilde {\M {P}}
= \mathcal {R} \SB {\M {P}}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\M {P}} ^\Adj
= \mathcal {R} \SB {\M {P} ^\Adj}
\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
%
\tilde {\V {z}}
= \mathcal {R} \SB {\V {z}}
\in \mathbb {R} ^{2 N_B^2} 
}
%
so, by construction,
%
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}
%
And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.

@@

\subsection {Plots of assorted methods}

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H} and \m {N_B}.

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-square-small-error.png}
\caption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-square-medium-error.png}
\caption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-square-big-error.png}
\caption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-small-error.png}
\caption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-medium-error.png}
\caption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-big-error.png}
\caption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-wide-small-error.png}
\caption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-wide-medium-error.png}
\caption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-wide-big-error.png}
\caption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
\end {figure}

As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {assorted-narrow-medium-time.png}
\caption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
\end {figure}

\subsection {Plots of DS only}

Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
Here, \m {\tilde {\chi}} is shown too.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-small-error.png}
\caption {DS, \m {N_B = 10, N_H = 12}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-medium-error.png}
\caption {DS, \m {N_B = 15, N_H = 18}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-big-error.png}
\caption {DS, \m {N_B = 20, N_H = 24}, error.}
\end {figure}
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {ddss-narrow-medium-time.png}
\caption {DS, \m {N_B = 15, N_H = 18}, time.}
\end {figure}

\subsection {Plots of OMP only}

Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.

%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-small-error.png}
\caption {OMP, \m {N_H = 12, N_B = 12}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-medium-error.png}
\caption {OMP, \m {N_H = 18, N_B = 18}, error.}
\end {figure}
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-big-error.png}
\caption {OMP, \m {N_H = 24, N_B = 24}, error.}
\end {figure}
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
%
\begin {figure} [hbt]
\includegraphics [width = \textwidth] {oommpp-square-medium-time.png}
\caption {OMP, \m {N_H = 18, N_B = 18}, time.}
\end {figure}

@@

On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
They gave
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2 \log N_B} 
}
%
Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathcal {O} \SB {N_H^2}}.

>>>>

\DispNum {y:y:Ry:Ny} {
\tilde {\V {y}}
= \mathcal {R} \SB {\V {y}}
\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} \\
%
\tilde {\V {g}}
= \mathcal {R} \SB {\V {g}}
\in \mathbb {R} ^{2 N_H^2} \\
%
\tilde {\M {P}}
= \mathcal {R} \SB {\M {P}}
\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \\
%
\tilde {\M {P}} ^\Adj
= \mathcal {R} \SB {\M {P} ^\Adj}
\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \\
%
\tilde {\V {z}}
= \mathcal {R} \SB {\V {z}}
\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} 
}
%
so, by construction,
%
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}
%
And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.

@@

\subsection {Plots of \m {N_H = 6}}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-square-two.png}
\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-tall-two.png}
\caption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-wide-two.png}
\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-square-four.png}
\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-tall-four.png}
\caption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-wide-four.png}
\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}
\end {figure}

\subsection {Plots of \m {N_H = 12}}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-square-two.png}
\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-tall-two.png}
\caption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-wide-two.png}
\caption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-square-four.png}
\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-tall-four.png}
\caption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-wide-four.png}
\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 12}, with \m {4} stages, error.}
\end {figure}

\subsection {Plots of \m {N_H = 18}}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-square-two.png}
\caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-tall-two.png}
\caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-wide-two.png}
\caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {2} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-square-two.png}
\caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-tall-two.png}
\caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-wide-two.png}
\caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {4} stages, error.}
\end {figure}

\subsection {Plots of runtime}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-small-square-two.png}
\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, time.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-medium-square-two.png}
\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, time.}
\end {figure}

\begin {figure} [hbt]
\includegraphics [width = \textwidth] {error-big-square-two.png}
\caption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, time.}
\end {figure}

@@

On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
They gave
%
\DispNum {C:P:ON:NY} {
C_{\mathrm {OMP}}
=\mathcal {O} \SB {N_H^2 \log \R {N_{B,t} N_{B,r}}} 
}
%
Here \m {\log N_{B,t}, \log N_{B,r}} are small in our experiments, and if we drop them we may assume \m {\mathcal {O} \SB {N_H^2}}.
